%-------------------------
% Resume in Latex
% Author : Daniel Mauricio Flores Sanchez
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\usepackage{soul}
\input{glyphtounicode}


%---------- FONT OPTIONS ----------
% sans-serif
\usepackage[sfdefault]{FiraSans}
\usepackage[sfdefault]{roboto}
\usepackage[sfdefault]{noto-sans}
\usepackage[default]{sourcesanspro}


% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-4pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \small#2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeVisaStatusHeading}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}
    \textit{\small#5}
}

\newcommand{\resumeEducationHeading}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}
    \textit{\small#5}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%---------- HEADING ----------

\begin{center}
    \texttt{\Huge \scshape Daniel Mauricio Flores} \\ \vspace{0pt}
    \textmd{Full-Stack Software Engineer --- ex: Criteo, IBM} \\ \vspace{10pt}
    \small
    \faMobile \hspace{.5pt} \href{tel:330749127211}{+330749127211}
    $|$
    \faEnvelopeO \hspace{.5pt} \href{mailto:dnielfs@gmail.com}{dnielfs@gmail.com}
    $|$
    \faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/devniel}{LinkedIn}
    $|$
    \faGithub \hspace{.5pt} \href{https://github.com/devniel}{GitHub}
    $|$
    \faGlobe \hspace{.5pt} \href{https://devniel.com}{devniel.com}
    $|$
    \faMapMarker \hspace{.5pt} {Paris, France}
\end{center}

%----------- EMPLOYMENT -----------
\section{Employment}
  \vspace{5pt}
  \resumeSubHeadingListStart

    \resumeSubheading
    {Criteo}{CDI / Jan 2020 \textbf{--} June 2024}
    {Software Engineer II}{Paris, France}
    \vspace{8pt}

    \resumeSubSubheading{\textbf{Criteo Relook AI} · OpenAI GPT-4o, Python, React, Next.js, TypeScript }{}
      \resumeItemListStart
        \resumeItem{\textbf{Prompt-a-dashboard}: An experimentation to generate dashboards by using text prompts, it relies on OpenAI GPT-4o to generate data based on a JSON schema compatible with the Criteo Relook Framework, this schema allows to define the views (tables, charts, texts), layout structure and static datasets which Relook will render as an editable dashboard.}
        \resumeItem{\textbf{Draw-a-dashboard}: The initial version of Text-to-dashboard. A drawing is converted by OpenAI GPT-4o into a JSON object which is parsed by the Relook framework to produce an editable UI.}
        \resumeItem{Video: {\href{https://youtu.be/to4aKOdhpgQ}{\color{blue}https://youtu.be/to4aKOdhpgQ}}}
        \resumeItem{Technologies: Prompt engineering, Python, OpenAI GPT-4o, React, Next.js, Excalidraw.}
        \resumeItemListEnd

    \resumeSubSubheading{\textbf{Criteo Analytics} · TypeScript, React, Scala, C\# }{}
      \resumeItemListStart
        \resumeItem{Development of data visualization solutions such as dashboards and reporting tools for Criteo's advertisers, allowing them to track and measure the performance of advertising campaigns and understanding of their customers behavior. Technologies: Scala, C\#, React, Angular, GraphQL, TypeScript, MaterialUI, MariaDB, Vertica, Cypress and Jest.}
        \resumeItem{Development and maintenance of Relook, a React framework to create dashboards.}
        \resumeItem{Development and maintenance of the Relook Design System, a React implementation of the Criteo Design System (Angular) with a catalog of components such as Dashboard, DatePicker, Table and Inputs used by the Relook framework and other internal projects. Technologies: React, MaterialUI, Typescript, Storybook and Webpack.}
        \resumeItem{Developed endpoints for the public analytics API using C\# and Criteo .NET stack, allowing clients to access their reports in a programmatic way. URL: {\href{https://developers.criteo.com/marketing-solutions/reference/getadsetreport}{\color{blue}https://developers.criteo.com/marketing-solutions/reference/getadsetreport}}
        }
        \resumeItem{Mentorship and support to newcomers to help them quickly adapt to the team's requirements and the Criteo ecosystem.}
        \resumeItemListEnd
    
    \resumeSubSubheading{\textbf{Criteo Connect} · TypeScript, Next.js, Node.js }{}
      \resumeItemListStart
        \resumeItem{Development of an internal social app to connect Criteo employees and visualize offices via a global map. Users can provide their workplace location, share more about themselves, add their interests and search colleagues nearby with the same hobbies. The project started as a hackathon idea winner, then across 2023 an MVP was developed by volunteers and presented to the HR leaders. Technologies: Next.js, Gradle, React, Redux, Node, MariaDB, TypeORM, Leaflet, Object Storage, Python and GIS.}
        \resumeItemListEnd
      
      \resumeSubSubheading{\textbf{Criteo Visual Search} · TypeScript, Python, Next.js }{}
        \resumeItemListStart
          \resumeItem{Development of the Visual Search app UI, an application to search products in the Criteo internal products catalog by using an image input; interacting with different machine learning models available via a REST API.
          Technologies: Next.js, Gradle, React, Redux, Python, Node.}
          \resumeItemListEnd

    \resumeSubSubheading{\textbf{Criteo Developers} · TypeScript, Svelte }{}
      \resumeItemListStart
        \resumeItem{Development of the Criteo Developers portal, onboarding hundreds of clients and scoring 92/100 in Google Lighthouse stats for desktop; built with Svelte, applying responsive design, accessibility, and SEO techniques; including a build system to generate the snippets to export to the Readme platform.
        \\[1.5pt]
        URL: {\href{https://developers.criteo.com}{\color{blue}https://developers.criteo.com}}
        }
      \resumeItemListEnd

    \resumeSubSubheading{\textbf{Criteo Prestashop Plugin} · Angular, PHP}{}
      \resumeItemListStart
        \resumeItem{Development of the WYSIWYG ad banner editor for the Criteo plugin providing a self-service way to configure and launch Criteo campaigns via Prestashop. Technologies: AngularJS, NGXS, Jest, Cypress, Puppeteer and NodeJS.}
        \resumeItem{Migration of a jQuery/smarty app to Angular. Technologies: PlantUML, Vega-Lite, AngularJS, JavaScript.}
      \resumeItemListEnd

    \resumeSubSubheading{\textbf{Other projects} }{}
      \resumeItemListStart
        \resumeItem{Contributing to Creative Foundry, proposal to generate advertising banners using AI.}
        \resumeItem{Contributed to translation process, migrating projects' string interpolations (Angular, React) to the ICU MessageFormat.}
        \resumeItem{Contributed to VizSQL, a scala SQL parser.}
        \resumeItem{Promoting the usage of Next.js in internal projects, sharing Gradle templates to make it easy with the Criteo tech stack.}
        \resumeItem{Speaker at the Frontend CriteoTech Meetup 2024: {\href{https://www.meetup.com/criteotech-meet-paris/events/300901350/}{\color{blue}https://www.meetup.com/criteotech-meet-paris/events/300901350/}}}
      \resumeItemListEnd

    \resumeSubheading
    {IBM}{May 2014 \textbf{--} Dec 2019}
    {Software Engineer}{Lima, Perú}
    \vspace{8pt}

      \resumeSubSubheading{\textbf{IBM Decision Advisor}  · React, GraphQL, Node.js}{}
        \resumeItemListStart
          \resumeItem{Implementation of the front-end software architecture to handle maintainability, reusability and data communication across the pages and components of the web app using React, Redux and GraphQL.}
          \resumeItem{Developed the Testing Automation roadmap and platform to improve the QA process using IBM DevOps, Travis and Testcafé, integrating it with the CI/CD pipeline.}
          \resumeItem{Contributions to Carbon components, a React implementation of the IBM Design System.
          \\[1.5pt] URL: {\href{https://www.ibm.com/services/technology/decision-advisor}{\color{blue}https://www.ibm.com/services/technology/decision-advisor}}
          }
        \resumeItemListEnd

      \resumeSubSubheading{\textbf{SUNAT Sofia, government chatbot on web and Facebook Messenger} · React, Node.js}{}
        \resumeItemListStart
          \resumeItem{Implemented the full-stack software architecture of Sofía, a government chat bot that helps citizens to solve questions about taxes, using React, Redux, Node.js, Socket.io, Redis, MongoDB and IBM Cloud.
          \\[1.5pt] URL: {\href{https://renta.sunat.gob.pe/personas/quienes-deben-declarar-el-impuesto-la-renta}{\color{blue}https://renta.sunat.gob.pe/personas/quienes-deben-declarar-el-impuesto-la-renta}}
          }
        \resumeItemListEnd

      \resumeSubSubheading{\textbf{Arturito BCP, first banking chatbot in Perú available on Facebook Messenger} · React, Node.js}{}
        \resumeItemListStart
          \resumeItem{Implemented the front-end and back-end software architecture with speech-to-text features, analytics and integration with external system of records using Node.js, Facebook Messenger Platform and IBM Cloud services. 36K likes and more than two million banking operations from 2016 to 2020.
          \\[1.5pt] URL: {\href{https://www.facebook.com/ArturitoBCP/}{\color{blue}https://www.facebook.com/ArturitoBCP/}}
          }
        \resumeItemListEnd

      \resumeSubSubheading{\textbf{PECSA GAS, SAP Mobile app connected to SAP ERP} · SAPUI5, Hybrid Mobile App Development}{}
        \resumeItemListStart
          \resumeItem{Developed hybrid SAP mobile apps to support the sale and distribution of gas done by the PECSA carriers, the mobile solution included connection to SAP ERP (via SAP SMP services) and receipts printing via Bluetooth connection to Zebra printers. Other technologies provided by SAP where used such as SAP Kapsel and \textbf{SAPUI5} with OData and a customized Apache Cordova plugin for the Zebra printers connection.
          \\[1.5pt] Video: {\href{https://youtube.com/shorts/\_LhR6XTVP5E}{\color{blue}https://youtube.com/shorts/\_LhR6XTVP5E}}}
        \resumeItemListEnd

      \resumeSubSubheading{\textbf{Other projects} }{}
        \resumeItemListStart
          \resumeItem{Support for Hackathons organized and/or sponsored by IBM in Perú by mentoring or giving talks.}
          \resumeItem{Davivienda chatbots: using Node.js, React, ES6, MongoDB and IBM Cloud services.}
          \resumeItem{RIMAC Procurator: development of native Android application using RxJava.}
          %\resumeItem{PECSAGAS Apps: hybrid SAP mobile apps using SAP Kapsel, SAPUI5, Cordova, OData and Zebra printers.}
          \resumeItem{PRIMAX GO: development of native Android applications using Java.}
          \resumeItem{BCP Home Banking: prototype development of the bank's new UI using jQuery, HTML5 and CSS3.}
        \resumeItemListEnd

  \resumeSubHeadingListEnd

\vspace{3pt}

%----------- AWARDS & ACHIEVEMENTS -----------

\section{Awards \& Achievements}
  \vspace{2pt}
  \resumeSubHeadingListStart
      \resumeProjectHeading
      {\textbf{Criteo Hackathon 2023 Winner - Creative Foundry}}{}
        \resumeItemListStart
          \resumeItem{Solution to assist and generate advertising banners using OpenAI ChatGPT and Stable Diffusion models. In charge of the API development to integrate the cloud or internal AI services. Technologies: C\#, Angular, Next.js, Replicate.com and OpenAI API.}
        \resumeItemListEnd

      \resumeProjectHeading
      {\textbf{IBM Advocate recognition at the IBM DBG Latin America Town Hall}}{}
        \resumeItemListStart
          \resumeItem{Acknowledge for embracing the IBM values and investing energy in supporting developers to disrupt their industries and differentiate in the market with the IBM technology.}
        \resumeItemListEnd

      \resumeProjectHeading
      {\textbf{IBM Perú - 4Q 2016 recognition}}{}
        \resumeItemListStart
          \resumeItem{For following the IBM's purpose, value and practices in 2016. Important projects, where I participated, were also recognized : Arturito BCP (main engineer) and PECSAGAS - SAP Business on HANA (mobile engineer).}
        \resumeItemListEnd

      \resumeProjectHeading
      {\textbf{IBM Volunteer Excellence Award 2015}}{}
        \resumeItemListStart
          \resumeItem{"The IBM Volunteer Excellence Award is recognition from IBM Chairman and CEO Ginni Rometty, and is the highest form of global volunteer recognition given by the company to employees. IBM volunteers from 13 countries – nine teams and four individuals – were honored as those who best exemplify the IBM values of dedication, innovation and trust in their volunteer projects. These volunteers live IBM’s practices by using their skills and expertise to engage and impact communities throughout the globe. Their impressive impact leveraged IBM strategic technologies (Bluemix, Analytics, SPSS) to solve critical community issues." (Project: Pondetuparte.com)
          \\[1.5pt] Badge: {\href{https://www.credly.com/badges/3cc80139-80af-4f95-98c9-49557e77869c/public\_url}{\color{blue}https://www.credly.com/badges/3cc80139-80af-4f95-98c9-49557e77869c/public\_url}}
          }
        \resumeItemListEnd


      \resumeProjectHeading
      {\textbf{IV Systems Engineering Faculty Research Competition}}{}
        \resumeItemListStart
          \resumeItem{Best research project: Notephy.com, an online whiteboard to share notes with the main capability of replaying them; a pastebin for handwriting notes.}
        \resumeItemListEnd

  \resumeSubHeadingListEnd

%----------- VISA STATUS -----------

\section{Visa status}
  \vspace{3pt}
  \resumeSubHeadingListStart
    \resumeVisaStatusHeading
      {Passeport talent : Carte Bleue Européenne}{Paris, France}
      {04/01/2024 - 03/01/2028}{}
      {}
      {}
\resumeSubHeadingListEnd

%----------- EDUCATION -----------

\section{Education}
  \vspace{3pt}
  \resumeSubHeadingListStart
    \resumeEducationHeading
      {University of Lima}{Lima, Perú}
      {Bachelor of Science in Systems Engineering. \textbf{GPA: 4.0}}{Aug 2008 \textbf{--} Jun 2014}
      {Trainee in the IT Department \& Research office to develop a Learning Management System using Play Framework 2.0 (Java, Scala).}
      {}
  \resumeSubHeadingListEnd

%----------- PROJECTS -----------

\section{Other projects}
    \vspace{3pt}
    \resumeSubHeadingListStart

      \resumeProjectHeading
      {\textbf{Sencha - generation of stories using AI, done for the Mistral Hackathon (2024)}}{}
        \resumeItemListStart
          \resumeItem{Technologies: Python, Flask, Next.js, React, TypeScript, Turborepo, MaterialUI, TailwindCSS, Poetry, StabilityAI Stable Diffusion API, Eleven Labs Voice API, Mistral API, OpenAI API, Amazon AWS EC2, Vercel, Groq.}
          \resumeItem{Post: \emph{\href{https://www.linkedin.com/posts/devniel\_sencha-activity-7200527122824671232-osP9}{\color{blue}https://www.linkedin.com/posts/devniel\_sencha-activity-7200527122824671232-osP9}}}
          \resumeItem{Demo: \emph{\href{https://sencha.devniel.com}{\color{blue}https://sencha.devniel.com}}}
        \resumeItemListEnd

      \resumeProjectHeading
        {\textbf{Tito XI - video created with generative AI (2023)}}{}
          \resumeItemListStart
            \resumeItem{Cinematic video created with generative AI technologies such as Midjourney Image generation, RunwayML Text/Image to Video and ElevenLabs Generative Voice; edited with Epidemic Sound and Davinci Resolve.}
            \resumeItem{Video: \emph{\href{https://www.youtube.com/watch?v=RQYhDdp8F2Q}{\color{blue}https://www.youtube.com/watch?v=RQYhDdp8F2Q}}}
          \resumeItemListEnd

      \resumeProjectHeading
      {\textbf{Message Formatter AI (2023)}}{}
        \resumeItemListStart
          \resumeItem{An experiment of ICU MessageFormat generation using OpenAI ChatGPT.}
          \resumeItem{Demo: \emph{\href{https://messageformatter.vercel.app/}{\color{blue}https://messageformatter.vercel.app/}}}
        \resumeItemListEnd

      \resumeProjectHeading
      {\textbf{NestJS Typeorm Testing (2019)}}{}
        \resumeItemListStart
          \resumeItem{NPM module to provide testing utilities for NestJS/Typeorm.}
          \resumeItem{URL: \emph{\href{https://www.npmjs.com/package/@devniel/nestjs-typeorm-testing/}{\color{blue}https://www.npmjs.com/package/@devniel/nestjs-typeorm-testing/}}}
        \resumeItemListEnd

      \resumeProjectHeading
        {\textbf{Proyecto Educativo Nacional al 2036 (2019)}}{}
          \resumeItemListStart
            \resumeItem{Volunteering work with the Peruvian government to process more than 220K survey replies of citizens across all the territory, using IBM Watson services to generate indicators and React, Node, Typescript to create a dashboard.}
            \resumeItem{Press (cached): \emph{\href{https://webcache.googleusercontent.com/search?q=cache:wUQDWn4Asn4J:https://andina.pe/agencia/noticia-usan-inteligencia-artificial-para-formular-proyecto-educativo-nacional-al-2036-777369.aspx&hl=en&gl=fr}{\color{blue}https://andina.pe/agencia/noticia-usan-
            inteligencia-artificial-para-formular-proyecto-educativo-nacional-al-2036-777369.aspx}} }
          \resumeItemListEnd
      
      \resumeProjectHeading
        {\textbf{Pondetuparte.com (2014-2017)}}{}
          \resumeItemListStart
            \resumeItem{Volunteering work with the Peruvian government for the 2014 United Nations Climate Change Conference. Social network to share pictures about eco-challenges; Technologies: Node, AngularJS, HTML, CSS, PHP and JavaScript.}
            \resumeItem{Web (archived): \emph{\href{https://web.archive.org/web/20160221121538/http://www.pondetuparte.com/}{\color{blue}https://web.archive.org/web/20160221121538/http://www.pondetuparte.com/}} }
            
          \resumeItemListEnd
      
      \resumeProjectHeading
        {\textbf{Notephy (2012)}}{}
          \resumeItemListStart
            \resumeItem{Online whiteboard for sharing and replaying handwritten notes. HTML5, JavaScript, Node, MongoDB, AWS, Facebook API, Canvas.}
            \resumeItem{Pitch video: \emph{\href{https://youtu.be/yxuK9CB6QDE?si=sfxBR3FpszYgRwC1}{\color{blue}https://youtu.be/yxuK9CB6QDE?si=sfxBR3FpszYgRwC1}} }
            
          \resumeItemListEnd

      \resumeProjectHeading
        {\textbf{SchedUL (2011)}}{}
          \resumeItemListStart
            \resumeItem{Facebook app to import and share the University of Lima students' schedules. Facebook SDK, PHP, HTML5, JavaScript, Web Scraping.}
          \resumeItemListEnd
      
    \resumeSubHeadingListEnd

%----------- SKILLS -----------

\section{Skills \& Languages}
\vspace{2pt}
\resumeSubHeadingListStart
  \small{\item{
      \textbf{Programming languages:}{ Typescript, JavaScript, Scala, C\#, Java, Python, PHP, CSS3, HTML5, SQL, LaTeX} \\ \vspace{3pt}
      \textbf{Frameworks, libraries and tools:}{ Next.js, React, Node, Svelte, Angular, RxJS, Playwright, NestJS, NGXS, Gerrit, PlantUML, UML,
      styled-components, Redux, Webpack, Cypress, Testcafé, Travis, Docker, Jest, Mocha, GraphQL, Apollo, Sass,
      Neo4j, MongoDB, PostgreSQL, MySQL, SAPUI5, XML, JSON, Git, Babel, NPM, Socket.IO, Redis, MQ, IBM Cloud, IBM
      Watson Assistant, Facebook Messenger Chatbots, Web Chatbots, Davinci Resolve, Adobe Photoshop.} \\ \vspace{3pt}
      \textbf{AI related:} {Stable Diffusion, Midjourney, OpenAI API, RunwayML, Video production with AI.} \\ \vspace{3pt}
      \textbf{Learning:}{ RAG, Local LLM models, ComfyUI, LlamaIndex, LangChain, Llama 3, LLaVA, Gemma, Ollama, Vector Databases, FAISS } \\ \vspace{3pt}
      \textbf{Languages:}{ English (Fluent), French (Intermediate), Spanish (Native)} \\ \vspace{3pt}
      % \textbf{Frameworks}{: X, X, X} \\
      % \textbf{Developer Tools}{: X, X, X} \\
      % \textbf{Libraries}{: X, X, X} \\
      % \textbf{Applications}{: X, X, X}
  }}
\resumeSubHeadingListEnd

\end{document}
